---
title: "Final Project"
subtitle: "Data selection, Correlation and Distributions"
author: anonymous # <-- hand in anonymously
format: 
  html:
    toc: true
    code-tools: true
    code-line-numbers: true  
    number-sections: true
    mainfont: Georgia, serif
    page-layout: article
  pdf:  
    geometry:
    - left=1cm,top=1cm,bottom=1cm,right=7cm
    number-sections: true
    code-annotations: none
editor: source
---

# General information

No AI used in this assignment. 

:::: {.content-hidden when-format="pdf"}
::: {.callout-warning collapse=false}

The following loads several needed packages:

```{r}
#| label: imports

library(aaltobda)
library(bayesplot)
library(cmdstanr)
library(dplyr)
library(ggplot2)
library(ggdist) # for stat_dotsinterval
library(posterior)
if(!require(brms)){
    install.packages("brms")
    library(brms)
}

# Set more readable themes with bigger font for plotting packages.
ggplot2::theme_set(theme_minimal(base_size = 14))
bayesplot::bayesplot_theme_set(theme_minimal(base_size = 14))

# This registers CmdStan as the backend for compiling cmdstan-chunks.
check_cmdstan_toolchain(fix = TRUE, quiet = TRUE)
register_knitr_engine(override = FALSE)
```

# installations
```{r}
#install.packages("readxl")
#install.packages("corrplot")
#install.packages("psych")
#install.packages("stats")
#install.packages("ltm")
#install.packages("caret") # confusion matrix -> F1
#install.packages("xtable"). # latex output
```

# Load the packages
```{r}
library(readxl)
library(corrplot)
#library(psych)
library(ltm)
library(caret)
library(xtable)
```

:::
::::

# Credit Card Data 


## Uploading data
```{r}
#file_path <- "default-credit-card.xls"
#data <- read_excel(file_path)
file_path_credit <- "default-credit-card.csv"
file_path_credit_names <- "names-default-credit-card.csv"
data_credit <- read.csv(file_path_credit)
data_credit_names <- read.csv(file_path_credit_names)

credit_short_colnames <- colnames(data_credit)
credit_long_colnames <- colnames(data_credit_names)

# Display the contents of the data frame
colnames(data_credit) <- credit_long_colnames
print(head(data_credit))
#colnames(data_credit) <- credit_short_colnames
credit_long_colnames
credit_short_colnames
```

## data extraction
```{r}
file_path_credit <- "default-credit-card.csv"
file_path_credit_names <- "names-default-credit-card.csv"
data_credit <- read.csv(file_path_credit)
data_credit_names <- read.csv(file_path_credit_names)

credit_short_colnames <- colnames(data_credit)
credit_long_colnames <- colnames(data_credit_names)
colnames(data_credit) <- credit_long_colnames
#sort(unique(data_credit$EDUCATION))
#sort(unique(data_credit$PAY_0))
round(sort(unique(data_credit$LIMIT_BAL))/1000)
sort(unique(data_credit$PAY_0))
sort(unique(data_credit$PAY_2))

data_credit$LIMIT_BAL_BINS <- cut(data_credit$LIMIT_BAL, breaks = 10, labels = FALSE)
sort(unique(data_credit$LIMIT_BAL_BINS))

data_credit_unclean=data_credit

data_credit <- data_credit %>% 
  filter(PAY_0 != -2) %>% filter(PAY_0 != 0) %>% 
  filter(PAY_2 != -2)  %>% filter(PAY_2 != 0)  %>% 
  filter(PAY_3 != -2)  %>% filter(PAY_3 != 0)  %>% 
  filter(PAY_4 != -2)  %>% filter(PAY_4 != 0)  %>% 
  filter(PAY_5 != -2)  %>% filter(PAY_5 != 0)  %>% 
  filter(PAY_6 != -2)  %>% filter(PAY_6 != 0)  %>%
  filter(EDUCATION > 0) %>% filter(EDUCATION < 4)


data_credit_edu <-function(edu,def){data_credit %>% filter(EDUCATION == edu) %>% filter(default == def) %>% sample_n(40)}
data_limit_bins <-function(edu,def){data_credit %>% filter(LIMIT_BAL_BINS == edu) %>% filter(default == def) %>% sample_n(40)}

combined_df <- rbind(data_credit_edu(1,0), data_credit_edu(1,1),
                     data_credit_edu(2,0), data_credit_edu(2,1),
                     data_credit_edu(3,0), data_credit_edu(3,1)) 


#combined_df_limit_bal <- do.call(rbind, lapply(c(1, 2, 3, 4, 5, 6, 7, 8, 10), function(x) rbind(data_limit_bins(x, 0), data_limit_bins(x, 1))))
combined_df_limit_bal <- do.call(rbind, lapply(c(1, 2, 3,4,5), function(x) rbind(data_limit_bins(x, 0), data_limit_bins(x, 1))))


# not enough data for education = 4
#data_credit %>% filter(EDUCATION == 4) %>% filter(default == 1)

write.csv(combined_df, file = "credit_data_education_short.csv")

dim(data_credit)
data_credit_full = data_credit
data_credit = combined_df
data_credit_short_limit_bal = combined_df_limit_bal
sort(unique(data_credit$LIMIT_BAL_BINS))
```

## correlations in full dataset
```{r}


colnames(data_credit_full) <- credit_long_colnames
df = data_credit_full
#correlations <- sapply(df[, -which(names(df) == "Y")], function(x) cor.test(x, df$Y)$estimate)
#correlations <- sapply(df[, -which(names(df) == "Y")], function(x) biserial.cor(x, df$Y))
correlations <- sapply(df[, -which(names(df) == "default")], function(x) biserial.cor(x, df$default))
list_cor = sort(round(abs(correlations),3))
correlations_df <- data.frame(
  Variable = names(list_cor),
  Correlation = as.vector(list_cor)
)

# Display the correlation coefficients



data_credit_names
correlations_df %>% filter(Correlation > 0)

cor_matrix <- cor(data_credit[, -1])  

# Create a correlation matrix plot
#corrplot(cor_matrix, method = "number", type = "upper", order = "hclust", tl.col = "black", tl.srt = 45)
corrplot(cor_matrix, method = "color", type = "upper", order = "hclust", tl.col = "black", tl.srt = 45,cl.cex = 0.7,tl.cex =0.7,number.cex = 0.4)

title("Correlation Matrix Plot")
print(t(data_credit_names))

correlations <- cor(data_credit[, 'default'], data_credit[, -which(names(data_credit) == 'default')])

round(correlations,3)



```
## correlations
```{r}


colnames(data_credit) <- credit_long_colnames
df = data_credit
#correlations <- sapply(df[, -which(names(df) == "Y")], function(x) cor.test(x, df$Y)$estimate)
#correlations <- sapply(df[, -which(names(df) == "Y")], function(x) biserial.cor(x, df$Y))
correlations <- sapply(df[, -which(names(df) == "default")], function(x) biserial.cor(x, df$default))
list_cor = sort(round(abs(correlations),3))
correlations_df <- data.frame(
  Variable = names(list_cor),
  Correlation = as.vector(list_cor)
)

# Display the correlation coefficients



data_credit_names
correlations_df %>% filter(Correlation > 0)
```

```{r}
# Calculate the correlation matrix
cor_matrix <- cor(data_credit[, -1])  

# Create a correlation matrix plot
#corrplot(cor_matrix, method = "number", type = "upper", order = "hclust", tl.col = "black", tl.srt = 45)
corrplot(cor_matrix, method = "color", type = "upper", order = "hclust", tl.col = "black", tl.srt = 45,cl.cex = 0.7,tl.cex =0.7,number.cex = 0.4)

title("Correlation Matrix Plot")
print(t(data_credit_names))

correlations <- cor(data_credit[, 'default'], data_credit[, -which(names(data_credit) == 'default')])

round(correlations,3)

```


```{r}
df = data_credit[, -1]

col_names <- correlations_df %>% filter(Correlation > 0.07)  %>%  dplyr::select(Variable)

as.list(col_names$Variable)

hist(df$default)
#par(mfrow = c(1, ncol(df)))
#for (col in names(df)) {
for (col in as.list(col_names$Variable)) {
  hist(df[[col]], main = col, xlab = col, col = "skyblue", border = "black")
}
```


## Stan model PAY_0 + PAY_2
```{r}
#Time  1.36 mins
start.time <- Sys.time()
fit <- brm(default ~ PAY_0 + PAY_2,
            data = data_credit,
            refresh = 0,
            prior=c(
              prior(normal(0,100), class="Intercept"),
                prior(normal(0, 100), class = b)
            ),
            family = bernoulli(),
           file = "pooled",
           backend = "cmdstanr"
)
end.time <- Sys.time()
time.taken <- round(end.time - start.time,2)
time.taken
```
```{r}
#install.packages("ggExtra", dependencies = T)
library(ggExtra)
#Here we make a scatter plot with marginal densities.

p <-
  data_credit %>% 
  ggplot(aes(x = PAY_0, y = PAY_2, fill = default == 1)) +
  geom_point(aes(color = default == 1), 
             alpha = 2/3) +
  scale_color_manual(values = c("red4", "blue4")) +
  scale_fill_manual(values = c("red4", "blue4")) +
  theme(panel.grid = element_blank(),
        legend.position = "none")
p %>% 
  ggMarginal(data = data_credit,  
             groupFill = T,
             type = 'density', 
             color = "transparent")
             
```

```{r}
#print(fit)
#plot(fit)
#mcmc_pairs(fit)
summarize_draws(fit)
```
```{r}
start.time <- Sys.time()
predictions <- predict(fit, newdata = data_credit, type = "response")
end.time <- Sys.time()
time.taken <- round(end.time - start.time,2)
time.taken
```
```{r}
start.time <- Sys.time()
predictions_full <- predict(fit, newdata = data_credit_full, type = "response")
end.time <- Sys.time()
time.taken <- round(end.time - start.time,2)
time.taken
```
```{r}
start.time <- Sys.time()
predictions_unclean<- predict(fit, newdata = data_credit_unclean, type = "response")
end.time <- Sys.time()
time.taken <- round(end.time - start.time,2)
time.taken
```

```{r}
binary_predictions <- ifelse(predictions[,1] > 0.5, 1, 0)
library(caret)
conf_matrix <- confusionMatrix(factor(binary_predictions), factor(data_credit$default))
conf_matrix
```
```{r}
binary_predictions_full <- ifelse(predictions_full[,1] > 0.5, 1, 0)
conf_matrix <- confusionMatrix(factor(binary_predictions_full), factor(data_credit_full$default))
conf_matrix

(2104+1015)/4030
```
```{r}
binary_predictions_unclean <- ifelse(predictions_unclean[,1] > 0.5, 1, 0)
conf_matrix <- confusionMatrix(factor(binary_predictions_unclean), factor(data_credit_unclean$default))
conf_matrix

```

## Stan model (PAY_0 + PAY_2| EDUCATION) Hierarchical

```{r}
start.time <- Sys.time()
#fit2_education <- brm(default ~ 1 + (PAY_0| EDUCATION),    # full dataset  time ~??? > 4 min
#fit2_education <- brm(default ~ (1 + PAY_0| EDUCATION),     # first 1000 dataset time ~ terminated abnormally
#fit2_education <- brm(default ~ 1 + (PAY_0| EDUCATION),    # first 1000 dataset time ~terminated abnormally
#fit2_education <- brm(default ~ PAY_0 + (PAY_0| EDUCATION),    # first 100 dataset time ~ 44 sec
#fit2_education <- brm(default ~ PAY_0 + PAY_2 + (PAY_0 + PAY_2| EDUCATION),   # first 1000 dataset time ~ 1.45 min
#fit2_education <- brm(default ~ PAY_0 + PAY_2 + (PAY_0 + PAY_2| EDUCATION),   # first 10000 dataset time ~ 16.5 min
#fit2_education <- brm(default ~ PAY_0 + PAY_2 + (1| EDUCATION),   # shart dataset
#fit2_education <- brm(default ~ 1 + (PAY_0 + PAY_2| EDUCATION),   # shart dataset
#fit2_education <- brm(default ~ PAY_0 + PAY_2 + (PAY_0 + PAY_2| EDUCATION),   # shart dataset
#fit2_education <- brm(default ~  PAY_0 + PAY_2 + (1| EDUCATION),   # shart dataset
#fit2_education <- brm(default ~ (1| EDUCATION),   # short dataset
fit2_education <- brm(default ~ (PAY_0 + PAY_2| EDUCATION),   # shart dataset
            data = data_credit,
            refresh = 0,
            prior=c(
                prior(normal(0,100),  class="Intercept")
              #  ,
               # prior(normal(0, 100), class = b)
            ),
            family = bernoulli(),
            file = "model2_education_small_data_set",
            backend = "cmdstanr",
            iter = 5000,
            warmup = 2500
)
end.time <- Sys.time()
time.taken <- round(end.time - start.time,2)
time.taken

```
```{r}
prior_summary(fit2_education)
```

```{r}
# mean of posterior_predict is the same as predict
post_pred = colMeans(brms::posterior_predict(fit2_education))
predictions <- predict(fit2_education, newdata = data_credit, type = "response", allow_new_levels = TRUE)

#mean((post_pred - predictions[,1])/post_pred)
#-0.003031049

```
```{r}
predictions <- predict(fit2_education, newdata = data_credit, type = "response", allow_new_levels = TRUE)
binary_predictions <- ifelse(predictions[,1] > 0.5, 1, 0)
conf_matrix <- confusionMatrix(factor(binary_predictions), factor(data_credit$default))
conf_matrix
```

```{r}
start.time <- Sys.time()
batch_size = 1000;
start = 1;
binary_predictions_unclean = c();
for (i in 1:30) {
  if (i%%10 == 0) {
    print(i);
  }
  end = start + batch_size - 1;
  #print(start)
  #print(end)
  predictions_batch <- predict(fit2_education, newdata = data_credit_unclean[start:end,], 
                  type = "response", allow_new_levels = TRUE)
  start = end + 1
  binary_predictions_batch <- ifelse(predictions_batch[,1] > 0.5, 1, 0)
  binary_predictions_unclean = c(binary_predictions_unclean, binary_predictions_batch);
  #print(binary_predictions_full)
}

end.time <- Sys.time()
time.taken <- round(end.time - start.time,2)
time.taken
```
```{r}
#length(binary_predictions_unclean)
#length(data_credit_unclean$default)

conf_matrix <- confusionMatrix(factor(binary_predictions_unclean), reference = factor(data_credit_unclean$default))
conf_matrix
```

## Model comparison (e.g. with LOO-CV).


```{r}
fit1 = fit
fit2 = fit2_education
l1 = loo(fit1)
l2 = loo(fit2)
res = loo_compare(l1,l2)
res
xtable(res)

```
```{r}
plot(l1, label_points = TRUE, main = 'PSIS diagnostic plot for pooled model')
plot(l2, label_points = TRUE, main = 'PSIS diagnostic plot for hierarchical model')
```

## Convergence diagnostic  
```{r}
sum_fit1=summarize_draws(fit1)
sum_fit1
xtable(sum_fit1)
```
```{r}
sum_fit2=summarize_draws(fit2)
sum_fit2
xtable(sum_fit2)
```


# The rest of codes. 
## Stan model with Credit LIMIT_BAL_BINS No HIERARCHi
```{r}
#head(data_credit, n = 100)
```

```{r}
start.time <- Sys.time()
fit2_education <- brm(default ~ PAY_0 + PAY_2,   # shart dataset
            data = data_credit_short_limit_bal, #data_credit,
            refresh = 0,
            prior=c(
              prior(normal(0,100), class="Intercept")
              #prior(exponential(.02), class="sd"),#p(tau)
              #prior(exponential(.02), class="sigma") #p(sigma)
            ),
            family = bernoulli(),
     #       file = "model_limit_bal_bins",
            file = "model_limit_bal_bins_data_sort4bins_reg",
            backend = "cmdstanr"
)
end.time <- Sys.time()
time.taken <- round(end.time - start.time,2)
time.taken

```

```{r}
start.time <- Sys.time()
predictions <- predict(fit2_education, newdata = data_credit, type = "response", allow_new_levels = TRUE)
end.time <- Sys.time()
time.taken <- round(end.time - start.time,2)
time.taken
```
          
```{r}
binary_predictions <- ifelse(predictions[,1] > 0.5, 1, 0)
library(caret)

conf_matrix <- confusionMatrix(factor(binary_predictions), factor(data_credit$default))
conf_matrix
```

```{r}
start.time <- Sys.time()
predictions_full <- predict(fit, newdata = data_credit_full, type = "response")
end.time <- Sys.time()
time.taken <- round(end.time - start.time,2)
time.taken
```

```{r}
binary_predictions_full <- ifelse(predictions_full[,1] > 0.5, 1, 0)
conf_matrix <- confusionMatrix(factor(binary_predictions_full), factor(data_credit_full$default))
conf_matrix
```

```{r}
start.time <- Sys.time()
predictions_unclean<- predict(fit, newdata = data_credit_unclean, type = "response")
end.time <- Sys.time()
time.taken <- round(end.time - start.time,2)
time.taken
```
```{r}
binary_predictions_unclean <- ifelse(predictions_unclean[,1] > 0.5, 1, 0)
conf_matrix <- confusionMatrix(factor(binary_predictions_unclean), factor(data_credit_unclean$default))
conf_matrix

```


## Stan model with Credit LIMIT_BAL_BINS
```{r}
#head(data_credit, n = 100)
```

```{r}
start.time <- Sys.time()
#fit2_education <- brm(default ~ 1 + (PAY_0| EDUCATION),    # full dataset  time ~??? > 4 min
#fit2_education <- brm(default ~ (1 + PAY_0| EDUCATION),     # first 1000 dataset time ~ terminated abnormally
#fit2_education <- brm(default ~ 1 + (PAY_0| EDUCATION),    # first 1000 dataset time ~terminated abnormally
#fit2_education <- brm(default ~ PAY_0 + (PAY_0| EDUCATION),    # first 100 dataset time ~ 44 sec
#fit2_education <- brm(default ~ PAY_0 + PAY_2 + (PAY_0 + PAY_2| EDUCATION),   # first 1000 dataset time ~ 1.45 min
#fit2_education <- brm(default ~ PAY_0 + PAY_2 + (PAY_0 + PAY_2| EDUCATION),   # first 10000 dataset time ~ 16.5 min
fit2_education <- brm(default ~ PAY_0 + PAY_2 + (PAY_0 + PAY_2|LIMIT_BAL_BINS),   # shart dataset
            data = data_credit_short_limit_bal, #data_credit,
            refresh = 0,
            prior=c(
              prior(normal(0,100), class="Intercept")
              #prior(exponential(.02), class="sd"),#p(tau)
              #prior(exponential(.02), class="sigma") #p(sigma)
            ),
            family = bernoulli(),
     #       file = "model_limit_bal_bins",
            file = "model_limit_bal_bins_data_sort4bins",
            backend = "cmdstanr"
)
end.time <- Sys.time()
time.taken <- round(end.time - start.time,2)
time.taken

```

```{r}
start.time <- Sys.time()
predictions <- predict(fit2_education, newdata = data_credit, type = "response", allow_new_levels = TRUE)
end.time <- Sys.time()
time.taken <- round(end.time - start.time,2)
time.taken
```
          
```{r}
binary_predictions <- ifelse(predictions[,1] > 0.5, 1, 0)
library(caret)

conf_matrix <- confusionMatrix(factor(binary_predictions), factor(data_credit$default))
conf_matrix
```

```{r}
start.time <- Sys.time()
predictions_full <- predict(fit, newdata = data_credit_full, type = "response")
end.time <- Sys.time()
time.taken <- round(end.time - start.time,2)
time.taken
```

```{r}
binary_predictions_full <- ifelse(predictions_full[,1] > 0.5, 1, 0)
conf_matrix <- confusionMatrix(factor(binary_predictions_full), factor(data_credit_full$default))
conf_matrix
```

```{r}
start.time <- Sys.time()
predictions_unclean<- predict(fit, newdata = data_credit_unclean, type = "response")
end.time <- Sys.time()
time.taken <- round(end.time - start.time,2)
time.taken
```
```{r}
binary_predictions_unclean <- ifelse(predictions_unclean[,1] > 0.5, 1, 0)
conf_matrix <- confusionMatrix(factor(binary_predictions_unclean), factor(data_credit_unclean$default))
conf_matrix

```


## Stan model New
```{r}
#head(data_credit, n = 100)
```

```{r}
start.time <- Sys.time()
fit2_limit_bal <- brm(default ~ LIMIT_BAL,   # shart dataset
            data = data_credit,
            refresh = 0,
            prior=c(
              prior(normal(0,100), class="Intercept")
              #prior(exponential(.02), class="sd"),#p(tau)
              #prior(exponential(.02), class="sigma") #p(sigma)
            ),
            family = bernoulli(),
            file = "fit2_limit_bal",
            backend = "cmdstanr"
)
end.time <- Sys.time()
time.taken <- round(end.time - start.time,2)
time.taken

```

```{r}
start.time <- Sys.time()
predictions <- predict(fit2_limit_bal, newdata = data_credit, type = "response", allow_new_levels = TRUE)
end.time <- Sys.time()
time.taken <- round(end.time - start.time,2)
time.taken
```
          
```{r}
binary_predictions <- ifelse(predictions[,1] > 0.5, 1, 0)
conf_matrix <- confusionMatrix(factor(binary_predictions), factor(data_credit$default))
conf_matrix
```

```{r}
start.time <- Sys.time()
predictions_full <- predict(fit2_limit_bal, newdata = data_credit_full, type = "response",allow_new_levels = TRUE)
end.time <- Sys.time()
time.taken <- round(end.time - start.time,2)
time.taken
```
```{r}
binary_predictions_full <- ifelse(predictions_full[,1] > 0.5, 1, 0)
conf_matrix <- confusionMatrix(factor(binary_predictions_full), factor(data_credit_full$default))
conf_matrix
```


## Stan model New Hierarch
```{r}
#head(data_credit, n = 100)
```

```{r}
start.time <- Sys.time()
#fit2_limit_bal_h <- brm(default ~ PAY_0  + (LIMIT_BAL | PAY_0),
fit2_limit_bal_h <- brm(default ~ PAY_0  + (LIMIT_BAL | PAY_0), 
            data = data_credit,
            refresh = 0,
            prior=c(
              prior(normal(0,100), class="Intercept")
              #prior(exponential(.02), class="sd"),#p(tau)
              #prior(exponential(.02), class="sigma") #p(sigma)
            ),
            family = bernoulli(),
            #file = "fit2_limit_bal_h",
            backend = "cmdstanr"
)
end.time <- Sys.time()
time.taken <- round(end.time - start.time,2)
time.taken

```

```{r}
start.time <- Sys.time()
predictions <- predict(fit2_limit_bal_h, newdata = data_credit, type = "response", allow_new_levels = TRUE)
end.time <- Sys.time()
time.taken <- round(end.time - start.time,2)
time.taken
```
          
```{r}
binary_predictions <- ifelse(predictions[,1] > 0.5, 1, 0)
library(caret)
conf_matrix <- confusionMatrix(factor(binary_predictions), factor(data_credit$default))
conf_matrix
```

```{r}
start.time <- Sys.time()
predictions_full <- predict(fit2_limit_bal_h, newdata = data_credit_full, type = "response",allow_new_levels = TRUE)
end.time <- Sys.time()
time.taken <- round(end.time - start.time,2)
time.taken
```
```{r}
binary_predictions_full <- ifelse(predictions_full[,1] > 0.5, 1, 0)
conf_matrix <- confusionMatrix(factor(binary_predictions_full), factor(data_credit_full$default))
conf_matrix
```


## Customer behaviour data (Alternative dataset)
\textbf{Small Data set from [kaggle ](https://www.kaggle.com/datasets/denisadutca/customer-behaviour/)}


## Uploading data
```{r}
file_path_behaviour <- "customer-behaviour.csv"
data_behaviour <- read.csv(file_path_behaviour)

data_behaviour <- data_behaviour %>%
  mutate(Gender = as.integer(ifelse(Gender == "Male", 1, ifelse(Gender == "Female", 2, NA))))



print(head(data_behaviour))
```
## correlations features with target (Purchased)
```{r}

df = data_behaviour
correlations <- sapply(df[, -which(names(df) == "Purchased")], function(x) biserial.cor(x, df$Purchased))
list_cor = sort(round(abs(correlations),3))
correlations_df <- data.frame(
  Variable = names(list_cor),
  Correlation = as.vector(list_cor)
)

# Display the correlation coefficients

correlations_df %>% filter(Correlation > 0)
```
```{r}
df = data_behaviour[, -1]

col_names <- correlations_df %>% filter(Correlation > 0.01)  %>%  dplyr::select(Variable)

#as.list(col_names$Variable)

hist(df$Purchased)
#par(mfrow = c(1, ncol(df)))
#for (col in names(df)) {
for (col in as.list(col_names$Variable)) {
  hist(df[[col]], main = col, xlab = col, col = "skyblue", border = "black")
}
```

```{r}
library(psych)

df <- data_behaviour[, -1]
# Create a scatterplot matrix
pairs.panels(df, pch = 16, col = "blue")
```
